Local simple connectedness of boundaries of hyperbolic groups

### 2020-04-23 paper.tex
Added references

In~\cite{gromov87}, Gromov showed that the boundary of a hyperbolic group is a
compact metric space with finite topological dimension. Beyond these basic
properties, and excepting the case when $G$ is the fundamental group of a
negatively curved smooth closed manifold, in which case $\boundary G$ is a
sphere, boundaries of hyperbolic groups tend to be wild, fractal-like objects.
In~\cite{kapovichkleiner00}, Kapovich and Kleiner ask the following question.

\todo{Survey of examples}

>>>>

In~\cite{gromov87}, Gromov showed that the boundary of a hyperbolic group is a
compact metric space with finite topological dimension. Beyond these basic
properties, and excepting the case when $G$ is the fundamental group of a
negatively curved smooth closed manifold, in which case $\boundary G$ is a
sphere, boundaries of hyperbolic groups tend to be wild, fractal-like objects.
Concrete examples include the Menger curve~\cite{benakli92}, which is the
generic case~\cite{champetier95}, Sierpinski compacta, which arise as
boundaries of fundamental groups of compact hyperbolic manifolds with non-empty
totally geodesic boundary, the universal Menger compacta of dimensions
2~\cite{dranishnikov99} and 3~\cite{dymaraosajda07}, and Pontryagin
surfaces~\cite{dranishnikov99}. See also~\cite{davisjanuszkiewicz91} for a
flexible method for constructing interesting high-dimensional boundaries.

In~\cite{kapovichkleiner00}, Kapovich and Kleiner ask the following question.
